Learning Auditory Similarities Between Instrumental Playing Techniques

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
comment on the name for the repository

For the sake of reproducibility, the code of the proposed method and the experimental protocol is available\footnote{https://github.com/mathieulagrange/paperSpontaneousSimilarity}. For convenience, the features (scattering and MFCCs) are also provided, but the software can be used to process audio data.

>>>>

For the sake of reproducibility, the code of the proposed method and the experimental protocol is available\footnote{https://github.com/mathieulagrange/paperSpontaneousSimilarity \vl{I would love a more memorable name. @writing}}. For convenience, the features (scattering and MFCCs) are also provided, but the software can be used to process audio data.
